Short-term neuronal and synaptic plasticity act in synergy for deviance detection in spiking networks

### 2022-12-27 paper-1/manuscript.tex
Rev sec Results:F4 in light of better analysis

Yet, as we saw in Figure \ref{fig4}c, the membrane voltages also differed between the two conditions. In order to assess the relative contribution of $V_{TA}$ to the increased dev response, we chose to focus exclusively on time points with higher firing probability in the dev sequence, discarding data points with equal or lower firing probability relative to the msc sequence. We then weighted the remaining contrasts in $V_{TA}$ and $V_m$ by the magnitude of the response difference, and summed across neurons. The resulting time courses, shown in Figure \ref{fig4}f, show how much these two measures contributed to the increased dev response. While thresholds were slighly lowered throughout the response, the membrane potential was dramatically increased. In relative terms (Figure \ref{fig4}g), $V_{TA}$ constituted a major driver of increased firing only right at the onset of the response, with later contributions amounting to less than 20\% of the total voltage difference. This pattern was consistent across networks and stimuli, as shown in Figure \ref{fig4}h. This indicates that adaptation initiated and dominated the increase in firing in the beginning, whereas the late response was enlarged primarily as a result of increased presynaptic excitation.

>>>>

Yet, as we saw in Figure \ref{fig4}c, the membrane voltages also differed between the two conditions. In order to assess the relative contribution of $V_{TA}$ to the increased dev response, we chose to focus exclusively on time points with higher firing probability in the dev sequence, discarding data points with equal or lower firing probability relative to the msc sequence. We then weighted the remaining contrasts in $V_{TA}$ and $V_m$ by the magnitude of the response difference, and summed across neurons. The resulting time courses, shown in Figure \ref{fig4}f, show how much these two measures contributed to the increased dev response. While thresholds were slighly lowered throughout the response, the membrane potential was dramatically increased. In relative terms (Figure \ref{fig4}g), $V_{TA}$ constituted a major driver of increased firing right at the onset of the response, as well as briefly towards the end of the response. A similar pattern emerged across networks and stimuli, as shown in Figure \ref{fig4}h. Here, only the initial response was driven mainly by $V_{TA}$, while later differences were largely explained by differences in $V_m$, leading to a relative TA contribution of less than 20\% on average. This indicates that adaptation initiated and dominated the increase in firing in the beginning, whereas the late response was enlarged primarily as a result of increased presynaptic excitation.
